### 2022-08-17 manuscript.Rmd

```{r, setup, include=FALSE}
# Load R packages
library(buildmer)
library(emmeans)
library(here)
library(knitr)
library(lme4)
library(lmerTest)
library(MASS)
library(scales)
library(papaja)
library(cowplot)
library(parallel)
library(reticulate)
library(tidyverse)
library(magrittr)

>>>>

```{r, setup, include=FALSE}
# Load R packages
library(buildmer)
library(emmeans)
library(here)
library(knitr)
library(lmerTest)
library(MASS)
library(scales)
library(papaja)
library(cowplot)
library(parallel)
library(reticulate)
library(tidyverse)
library(magrittr)
